---
title: "Breast Cancer Predictive Model"
author: "Armando Saavedra"
date: "3/22/2020"
output:
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
---



```{css, echo=FALSE}
.fluid.row.title{
  font-size: 2.9vw
}
h1{
  font-size:1.9vw;
  margin-top: 30px!important;
  margin-bottom: 15px!important;
  padding-top: 0px!important;
  padding-bottom: 0px!important;
  font-weight: bold;
  border-bottom: solid 1px black;
}

h2{
  margin-top: 30px!important;
  margin-bottom: 15px!important;
  padding-top: 0px!important;
  padding-bottom: 0px!important;
  font-size: 22px;
  font-weight: bold
}
p{
  display: block;
  margin-block-start: 1em;
  margin-block-end: 1em;
  margin-inline-start: 0px;
  margin-inline-end: 0px;
  
}

```


<style>
.list-group-item.active, .list-group-item.active:focus, .list-group-item.active:hover {
    background-color: black;
}
</style>

# Introduction

The goal of this project is to analyze spatial data summarizing the number of acidents in New york. The objective is to create a heat map where every zip code shows the number of car accidents.

The information base of this analysis comes from a dataset found in Kaggle that provides differents 



```{r,include = FALSE,message=FALSE, warning=FALSE,paged.print=TRUE}
library(readxl)

library(data.table)
library(ggplot2)
library(ggthemes)

```
# Data

```{r,results = "hide"}
data<-read.csv("C:/Users/dsaav/Documents/Projects/Datasets/Breast Cancer Prediction/data.csv",header = TRUE)
sum(is.na(data$ZIP.CODE))

```

# Main Statistics
```{r,message = FALSE,warning = FALSE}
summary(data)

```
```{r,message = FALSE,warning = FALSE}
dim(data)

```
```{r,message = FALSE,warning = FALSE}
str(data)

```

