---
title: "SQL Server Exercises "
author: "Armando Saavedra"
date: "3/22/2020"
output:
  html_document:
    toc: true
    toc_float: true
    theme: cosmo # cosmo, darkly, flatly,spacelab,united,yeti        
            #bootstrap, cerulean,journal,lumen, paper,readable,sandstone,simplex
    highlight: tango #kate, pygments, tango, monochrome,haddock 
                       #zenburn,  espresso,textmate
---



```{css, echo=FALSE}
.fluid.row.title{
  font-size: 2.9vw
}
h1{
  font-size:1.9vw;
  margin-top: 30px!important;
  margin-bottom: 15px!important;
  padding-top: 0px!important;
  padding-bottom: 0px!important;
  font-weight: bold;
  border-bottom: solid 1px black;
}

h2{
  margin-top: 30px!important;
  margin-bottom: 15px!important;
  padding-top: 0px!important;
  padding-bottom: 0px!important;
  font-size: 22px;
  font-weight: bold
}
p{
  display: block;
  margin-block-start: 1em;
  margin-block-end: 1em;
  margin-inline-start: 0px;
  margin-inline-end: 0px;
  
}

```





<style>
.list-group-item.active, .list-group-item.active:focus, .list-group-item.active:hover {
    background-color: black;
}
</style>



```{r,include = FALSE,message=FALSE, warning=FALSE,paged.print=TRUE}
library(readxl)

library(data.table)
library(ggplot2)
library(ggthemes)
library(table1)
library(dplyr)
library(dbplyr)

library(knitr)


library(DBI)
library(odbc)
library(RODBC)
#setwd("C:/Users/dsaav/Documents/Projects/R/Portfolio/Project 5")
```


# Introduction

The purpose of this project is to provide an example where data from SQL Server is linked to RStudio environment. There are situation where R users does not feel confortable working with SQL. To facilitated this problem R has different solutions to amelianate this inconvenience. On of this is to stablish a connection to SQL data provider, in this case SQL Server, and access the different tables included in the schema of the database. 




# Data Source
The data used for the porpose of this project comes from a blog located in github called [PostgreSQL Exercises](https://ozencb.github.io/postgresql-exercises/). The same way, some of the exercises exposed here comes from the same source. 


# Connection
```{r,message = FALSE,warning = FALSE,comment=NA}


# Establish connection to SQL Server
con <- dbConnect(odbc::odbc(),
                 Driver = "SQL Server",          # Or "ODBC Driver 17 for SQL Server"
                 Server = "Armando\\SQLEXPRESS",    # Replace with your server name
                 Database = "Booking",            # Replace with your database name
                 Trusted_connection="True"
)

```


# Data extraction

```{r,message = FALSE,warning = FALSE,comment=NA}
bookings<-tbl(con,in_schema("cd","Bookings"))%>%
  collect()

members<-tbl(con,in_schema("cd","members"))%>%
  collect()

facilities<-tbl(con,in_schema("cd","facilities"))%>%
  collect()

```



# Exercises 

### Where Statement
Produce a list of facilities that charge a fee to members and that fee is less thatn 150 of the monthly maintance cost.

```{sql,connection=con, output.var="charge_data"}
SELECT name, membercost, monthlymaintenance 
FROM cd.facilities
WHERE membercost>0 AND
      (membercost<monthlymaintenance/50)

```

```{r, echo=FALSE}
kable(head(charge_data))

```


### Case when Statement
Create a new field that list facilities as cheap and expensive. To do that use $100 as criteria.


```{sql,connection=con, output.var="case_data" }
SELECT name, 
	     CASE WHEN (monthlymaintenance > 100) THEN 'expensive'
	     ELSE 'cheap'
	     END AS cost
FROM cd.facilities;    

```


```{r, echo=FALSE}
kable(case_data)

```
### Filter Dates
Identify the name and last name fo the members who joined after June 2012.

```{sql,connection=con,output.var="date_data"}
select surname, firstname, joindate 
from cd.members
where joindate>='2012-06-01' 
```


```{r, echo=FALSE}
kable(head(date_data))

```

### Subquery
Get the first and last name of the last member who signed up.
```{sql,connection=con,output.var="max_data"}
SELECT firstname, surname, joindate
FROM cd.members
WHERE joindate = (SELECT max(joindate) 
			            FROM cd.members);  
		 
```


```{r, echo=FALSE}
kable(max_data)

```

### Inner Join
* Get the list of the first six records of the start times for bookings for the member named David

```{sql,connection=con,output.var="join_data"}
SELECT B.firstname,B.surname,A.starttime 
FROM cd.bookings AS A
INNER JOIN cd.members AS B
 ON B.memid = A.memid
WHERE B.firstname = 'David' AND 
      B.surname='Farrell'

```


```{r, echo=FALSE}
kable(head(join_data))

```

### Left Join
List all members and includes those who recommended them. Order by surname and firstname

```{sql,connection=con,output.var="outer_data"}
SELECT A.firstname as memfname, A.surname as memsname, B.firstname as recfname,                       B.surname as recsname
FROM cd.members AS A
LEFT OUTER JOIN cd.members AS B
 ON B.memid = A.recommendedby
ORDER BY memsname, memfname;  

```


```{r, echo=FALSE}
kable(outer_data)

```
