---
title: "Breast Cancer Predictive Model"
author: "Armando Saavedra"
date: "3/22/2020"
output:
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
---



```{css, echo=FALSE}
.fluid.row.title{
  font-size: 2.9vw
}
h1{
  font-size:1.9vw;
  margin-top: 30px!important;
  margin-bottom: 15px!important;
  padding-top: 0px!important;
  padding-bottom: 0px!important;
  font-weight: bold;
  border-bottom: solid 1px black;
}

h2{
  margin-top: 30px!important;
  margin-bottom: 15px!important;
  padding-top: 0px!important;
  padding-bottom: 0px!important;
  font-size: 22px;
  font-weight: bold
}
p{
  display: block;
  margin-block-start: 1em;
  margin-block-end: 1em;
  margin-inline-start: 0px;
  margin-inline-end: 0px;
  
}

```


<style>
.list-group-item.active, .list-group-item.active:focus, .list-group-item.active:hover {
    background-color: black;
}
</style>

# Introduction

The goal of this project is to analyze spatial data summarizing the number of acidents in New york. The objective is to create a heat map where every zip code shows the number of car accidents.

The information base of this analysis comes from a dataset found in Kaggle that provides differents 



```{r,include = FALSE,message=FALSE, warning=FALSE,paged.print=TRUE}
library(readxl)

library(data.table)
library(ggplot2)
library(ggthemes)

```
# Data

```{r,results = "hide"}
data<-read.csv("C:/Users/dsaav/Documents/Projects/Datasets/Breast Cancer Prediction/data.csv",header = TRUE)
sum(is.na(data$ZI))

```
```{r,message = FALSE,warning = FALSE}
for (i in 1:ncol(data)){
 print(paste(colnames(data)[i],"=", sum(is.na(data[,i]))))
  }

```


# Main Statistics
```{r,message = FALSE,warning = FALSE}
summary(data)

```
```{r,message = FALSE,warning = FALSE}
dim(data)

```
```{r,message = FALSE,warning = FALSE}
str(data)

```


```{r,message = FALSE,warning = FALSE}
data$diagnosis<-factor(data$diagnosis)

```




# Data Visualization

```{r,message = FALSE,warning = FALSE}
library(gridExtra)
library(stringr)
library(ggplot2)


# Assign the columns of interest to a variable
#target_variables <- colnames(data)[2:7]



mulplot<-function(df,vars){
  my_plots_list <-lapply(vars, function(each_variable) {
    ggplot(df, aes_string(each_variable,fill=data$diagnosis)) + # NOTE - aes_string rather than aes
      geom_density(alpha = 0.5,linetype = 1) +ggtitle(str_c(each_variable))+
      theme(text=element_text(size = 9),legend.key.size = unit(0.5, 'cm'))+
      labs(x = " Values", y = "Density",fill='R')
    })
  gridExtra::grid.arrange(grobs = my_plots_list, ncol = 2,widths=c(10,10))
  }


mulplot(data,colnames(data)[2:7])
mulplot(data,colnames(data)[8:13])
mulplot(data,colnames(data)[14:19])
mulplot(data,colnames(data)[20:25])
mulplot(data,colnames(data)[26:31])



```


