---
title: "Breast Cancer Predictive Model"
author: "Armando Saavedra"
date: "3/22/2020"
output:
  html_document:
    toc: true
    toc_float: true
    theme: cosmo # cosmo, darkly, flatly,spacelab,united,yeti        
            #bootstrap, cerulean,journal,lumen, paper,readable,sandstone,simplex
    highlight: tango #kate, pygments, tango, monochrome,haddock 
                       #zenburn,  espresso,textmate
---



```{css, echo=FALSE}
.fluid.row.title{
  font-size: 2.9vw
}
h1{
  font-size:1.9vw;
  margin-top: 30px!important;
  margin-bottom: 15px!important;
  padding-top: 0px!important;
  padding-bottom: 0px!important;
  font-weight: bold;
  border-bottom: solid 1px black;
}

h2{
  margin-top: 30px!important;
  margin-bottom: 15px!important;
  padding-top: 0px!important;
  padding-bottom: 0px!important;
  font-size: 22px;
  font-weight: bold
}
p{
  display: block;
  margin-block-start: 1em;
  margin-block-end: 1em;
  margin-inline-start: 0px;
  margin-inline-end: 0px;
  
}

```





<style>
.list-group-item.active, .list-group-item.active:focus, .list-group-item.active:hover {
    background-color: black;
}
</style>




# Introduction

The goal of this project is to analyze spatial data summarizing the number of acidents in New york. The objective is to create a heat map where every zip code shows the number of car accidents.

The information base of this analysis comes from a dataset found in Kaggle that provides differents 



```{r,include = FALSE,message=FALSE, warning=FALSE,paged.print=TRUE}
library(readxl)

library(data.table)
library(ggplot2)
library(ggthemes)

```
# Data

```{r,message = FALSE,warning = FALSE,comment=NA}
data<-read.csv("C:/Users/dsaav/Documents/Projects/Datasets/Breast Cancer Prediction/data.csv",
               header = TRUE)
print(sum(is.na(data$ZI)))

```


```{r,message = FALSE,warning = FALSE,comment=NA}
for (i in 1:ncol(data)){
 print(paste(colnames(data)[i],"=", sum(is.na(data[,i]))))
  }

```

```{r,message = FALSE,warning = FALSE,comment=NA}
head(data)

```



# Main Statistics
```{r,message = FALSE,warning = FALSE,comment=NA}
summary(data)

```
```{r,message = FALSE,warning = FALSE}
dim(data)

```
```{r,message = FALSE,warning = FALSE}
str(data)

```






```{r,message = FALSE,warning = FALSE,comment=NA}
data$diagnosis<-factor(data$diagnosis)

```




# Data Visualization

```{r,message = FALSE,warning = FALSE,comment=NA}
library(gridExtra)
library(stringr)
library(ggplot2)


# Assign the columns of interest to a variable
#target_variables <- colnames(data)[2:7]



mulplot<-function(df,vars){
  my_plots_list <-lapply(vars, function(each_variable) {
    ggplot(df, aes_string(each_variable,fill=data$diagnosis)) + # NOTE - aes_string rather than aes
      geom_density(alpha = 0.5,linetype = 1) +ggtitle(str_c(each_variable))+
      theme(text=element_text(size = 9),legend.key.size = unit(0.5, 'cm'))+
      labs(x = " Values", y = "Density",fill='RGIT')
    })
  gridExtra::grid.arrange(grobs = my_plots_list, ncol = 2,widths=c(10,10))
  }
```


```{r,message = FALSE,warning = FALSE,echo=FALSE}

mulplot(data,colnames(data)[2:7])
mulplot(data,colnames(data)[8:13])
mulplot(data,colnames(data)[14:19])
mulplot(data,colnames(data)[20:25])
mulplot(data,colnames(data)[26:31])


```


# Training and Testing Data

```{r,message = FALSE,warning = FALSE, comment=NA}

train_test<-function(df){
  set.seed(1)
  
  sample <- sample(c(TRUE, FALSE), nrow(df), replace=TRUE, prob=c(0.7,0.3))
  train  <- df[sample, ]
  test   <- df[!sample, ]
  results <- list(train,test)
  return(results)
}

results=train_test(data)
train<-results[[1]]
test<-results[[2]]

```


# Logistic Regression Model

```{r,message = FALSE,warning = FALSE,comment=NA}



library(ggplot2)
library(dplyr)

logistic<-glm(formula=diagnosis ~ ., data=train,family="binomial")


```



```{r,message = FALSE,warning = FALSE,comment=NA}

summary(logistic)

```
